### 2014-02-26 paper/concrete.tex
More nattering around.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\begin{lemma}[Erased-transition/transition simulation (ETTS)]
    For any state |C|, if |erase l C .-> delta|, then there exists a |C'| such that
    |erase l C' = delta| and |C .=> C'|.
\end{lemma}

Traditional TSNI is an easy corollary of this lemma.  Now we can state
the result:

\begin{theorem}
    Suppose we have a abstract specification language $L$ with machine
    states $|C|$, evaluation relation $|.->|$ and erasure function $e$.
    Furthermore we have a proof that this language fulfills termination
    sensitive non-interference: if $|C1| \approx_l |C2|$ and $|C1|
    |.->|^* |C1'|$, then there exists a $|C2'|$ such that $|C2| |.->|^*
    |C2'|$ and $|C1'| \approx_l |C2'|$.

    Next, suppose we have a language $L'$ with machine states $|Q|$,
    evaluation relation $|.->|'$ and erasure function $e'$.  Given
    functions $f^{-1} : |C -> Q|$ and $f : |Q -> C|$ relating machine
    states between $L$ and $L'$, obeying the conditions:

    \begin{itemize}
        \item $f$ is functorial over $l$-equivalence: if
            $|Q1| \approx'_l |Q2|$ then $f(|Q1|) \approx_l f(|Q2|)$.
    \end{itemize}

    (Probably $f^{-1} \circ f =
    id$ and $f^{-1} \circ e' \circ f = e$)  Then to show termination sensitive non-interference for $L'$,
    it suffices to show that for every evaluation rule $|Q| |.->|' |Q'|$
    it is either the case that $f(|Q|) |.->| f(|Q'|)$ or that
    \ldots
\end{theorem}

\begin{proof}
Our proof proceeds along the same lines as a traditional TSNI proof,
we simply must show \Red{Lemma~1} holds for our language.  We proceed by induction
over reduction derivations in the first step.

>>>>

\begin{lemma}[Erased-transition/transition simulation (ETTS)]
    For any state |C|, if |erase l C ..-> delta|, then there exists a |C'| such that
    |erase l C' = delta| and |C .=> C'|.
\end{lemma}

Traditional TSNI is an easy corollary of this lemma.  \Red{Need to argue
this is provable!} Now we can state the result:

\begin{theorem}
    Suppose we have a abstract specification language $L$ with machine
    states $|C|$, evaluation relation $|.->|$, erasure function $|erasef l|$,
    and a proof that ETTS holds.

    Next, suppose we have a language $L'$ with machine states $|C'|$,
    evaluation relation $|.->|'$ and erasure function $|erasef l|'$.  We demand that this
    language be related to $L$ in the following way:

    \begin{itemize}
        \item There are functions $f : |C' -> C|$ and $f^{-1} : |C -> C'|$ which is functorial
            over $l$-equivalences: e.g. if $|C| \approx'_l |C'|$ then
            $f(|C|) \approx_l f(|C'|)$ and vice versa.
    \end{itemize}

    Then ETTS holds for language $L'$.
\end{theorem}

\begin{proof}
We need to show that for all choices of $|C1'|$, there exists a $|C2'|$ with
the desired properties.  We proceed by induction on the erased-transition.
There are two cases.  In the first case, there is a one-to-one correspondence
between reduction relations in

Our proof proceeds along the same lines as a traditional TSNI proof,
we simply must show \Red{Lemma~1} holds for our language.  We proceed by induction
over reduction derivations in the first step.
